Bayesian inference of relative fitness on high-throughput pooled competition assays

### 2023-12-20 doc/_fitness_model.qmd
Add schematic diagram showing sources of uncertainty

To account for all these sources of uncertainty in a principled way, in the next
section, we develop a Bayesian inference pipeline.

>>>>

<span style="color: #912E27;">
@fig-01(C) shows schematically the sources of uncertainty accounted for by our
model. The first three sources---population composition, barcode read counts,
and barcode frequencies---all contribute to uncertainty source 1. Uncertainty
source 2 and 3 are depicted by the last two sources, respectively.
</span>
To account for all these sources of uncertainty in a principled way, in the next
section, we develop a Bayesian inference pipeline.
